Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-11-09 MDPI_submission.Rmd
Commit 2023-11-08 20:14
Commit 2023-11-09 04:14

header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}
   - \captionsetup[sub]{position=bottom, labelfont={bf, small, stretch=1.17}, labelsep=space, textfont={small, stretch=1.17}, aboveskip=6pt,  belowskip=-6pt, singlelinecheck=off, justification=justified}

#  - \captionsetup[sub]{position=bottom, labelfont={bf, small, stretch=1.17}, labelsep=space, textfont={small, stretch=1.5}, aboveskip=6pt,  belowskip=6pt, singlelinecheck=off, justification=justified}
#  \captionsetup[figure]{position=bottom, labelfont={bf, small, stretch=1.17}, labelsep=period, textfont={small, stretch=1.17}, aboveskip=6pt, belowskip=-6pt, singlelinecheck=off, justification=justified}

@@

<!-- ------------------------------------------------------------ -->

<!-- ## Figures, Tables and Schemes -->

<!-- All figures and tables should be cited in the main text as Figure \ref{fig:fig1},  -->
<!-- \ref{tab:tab1}, etc. To get cross-reference to figure generated by R chunks  -->
<!-- include the `\\label{}` tag in the `fig.cap` attribute of the R chunk:  -->
<!-- `fig.cap = "Fancy Caption\\label{fig:plot}"`. -->

<!-- ```{r fig1, echo=FALSE, fig.width=3, fig.cap="A figure added with a code chunk.\\label{fig:fig1}"} -->
<!-- x = rnorm(10) -->
<!-- y = rnorm(10) -->
<!-- plot(x, y) -->
<!-- ``` -->

<!-- When making tables using `kable`, it is suggested to use -->
<!-- the `format="latex"` and `tabl.envir="table"` arguments -->
<!-- to ensure table numbering and compatibility with the mdpi -->
<!-- document class. -->

<!-- ```{r tab1, echo=FALSE} -->
<!-- knitr::kable(mtcars[1:5, 1:3],  -->
<!--              format = "latex",  -->
<!--              booktabs = TRUE,  -->
<!--              caption = "This is a table caption. Tables should be placed in the  -->
<!--              main text near to the first time they are~cited.",  -->
<!--              align = 'ccc', centering = FALSE, -->
<!--              table.envir = "table", position = "H") -->
<!-- ``` -->

<!-- ## Formatting of Mathematical Components -->

<!-- If you want numbered equations use Latex and wrap in the equation environment: -->

<!-- \begin{equation} -->
<!-- a = 1, -->
<!-- \end{equation} -->

<!-- the text following an equation need not be a new paragraph. Please punctuate  -->
<!-- equations as regular text. -->

<!-- ```{comment} -->
<!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph. -->
<!-- ``` -->

<!-- # Discussion -->

<!-- Authors should discuss the results and how they can be interpreted in -->
<!-- perspective of previous studies and of the working hypotheses. The findings and -->
<!-- their implications should be discussed in the broadest context possible. Future -->
<!-- research directions may also be highlighted. -->

<!-- # Conclusion -->

<!-- This section is not mandatory, but can be added to the manuscript if the -->
<!-- discussion is unusually long or complex. -->

>>>>

header-includes:
   # - \usepackage{subfig}
   - \usepackage{subcaption}
   - \captionsetup[sub]{position=bottom, labelfont={bf, small, stretch=1.17}, labelsep=space, textfont={small, stretch=1.17}, aboveskip=6pt,  belowskip=-6pt, singlelinecheck=off, justification=justified}
   - \usepackage{placeins}

@@
